---
title: "Homework Module 1.4 Key"
output: html
---

### Your Name

### Date

In the questions below, use R code to answer questions. For any non-coding questions, give your answer as a comment.

Run this code chunk first, to load the tidyverse, and make the weather station data available as the variable `stationData`:



```{r}
library(tidyverse)
stationData<-read_csv("station-data.csv")

```



What is the difference between the data in the `day` and `running_day` columns? Illustrate the difference with a function we learned in class. If we're grouping by month, which would be more useful?

```{r}

# day refers to day in a year (e.g. 1-365), and running_day is day of the month

unique(stationData$day)

unique(stationData$running_day)

```

How is the time of day represented in the data. At what times of the day are measurements taken? Show the code used to arrive at the answer.

```{r}

# time is represented in military time.
# measurements are taken every three hours, starting at midnight

unique(stationData$hour)

```

Report the mean and standard deviation of the atmospheric pressure for every hour, of every day, of every month.

```{r}

stationData %>%
  group_by(month, running_day, hour) %>%
  summarize(meanPressure=mean(pressure, na.rm=TRUE), sdPressure=sd(pressure, na.rm=TRUE))


```

Report the mean and standard deviation of the temperature and wind speed at noon of every day of every month.

```{r}

stationData %>%
  filter(hour=="1200") %>%
  group_by(month, running_day) %>%
  summarize(avgTemp=mean(temp, na.rm=TRUE),
            sdTemp=sd(temp, na.rm=TRUE),
            avgWindSpeed=mean(wind_speed, na.rm=TRUE),
            sdWindSpeed=sd(wind_speed, na.rm=TRUE)
            )



```

Find the coldest and warmest days of the year (in month, day format).

```{r}

#coldest
stationData %>%
  select(month, running_day, temp) %>%
  arrange(temp) %>%
  head(1)

# August 29th

#warmest
stationData %>%
  select(month, running_day, temp) %>%
  arrange(desc(temp)) %>%
  head(1)

# December 9th

```

Add a column to the data frame that contains the temperature in Kelvins.

```{r}
# add 273 to celcius

stationData <- stationData %>%
  mutate(tempKelvin=temp+273)



```
