---
title: "Homework Module 1.4"
output: html
---

### Your Name

### Date

In the questions below, use R code to answer questions. For any non-coding questions, give your answer as a comment.

Run this code chunk first, to load the tidyverse, and make the weather station data available as the variable `stationData`:



```{r}
library(tidyverse)
stationData<-read_csv("station-data.csv")

```



What is the difference between the data in the `day` and `running_day` columns? Illustrate the difference with a function we learned in class. If we're grouping by month, which would be more useful?

```{r}



```

How is the time of day represented in the data. At what times of the day are measurements taken? Show the code used to arrive at the answer.

```{r}



```

Report the mean and standard deviation of the atmospheric pressure for every hour, of every day, of every month.

```{r}




```

Report the mean and standard deviation of the temperature and wind speed at noon of every day of every month.

```{r}





```

Find the coldest and warmest days of the year (in month, day format).

```{r}



```

Add a column to the data frame that contains the temperature in Kelvins.

```{r}




```
