---
title: "Practice Problems 1.2 Key"
format: html
---

Here are some practice problems to explore the penguins data set. First we need to load the penguin data set.

```{r}
library("palmerpenguins")

penguins
```

1.  What are the mean and standard deviation of bill length of the penguins?

```{r}
# create a variable that contains only the column for bill length

billLength<-penguins$bill_length_mm


# mean 

mean(billLength, na.rm=TRUE)

# standard deviation

sd(billLength, na.rm=TRUE)

```

2.  What are the mean and standard deviation of the body mass of the penguins?

```{r}
# create a variable that contains only the column for body mass

bodyMass<-penguins$body_mass_g

# mean

mean(bodyMass, na.rm=TRUE)

# standard deviation

sd(bodyMass, na.rm = TRUE)

```

3.  What is the mean and median flipper length of the penguins?

```{r}
# create a variable that contains only the column for flipper length

flipperLength<-penguins$flipper_length_mm

# mean

mean(flipperLength, na.rm=TRUE)

# median

median(flipperLength, na.rm=TRUE)
```

4.  How long are the largest flippers in this data set? How long is the shortest? (Hint: google how to find the minimum and maximum values in a vector). You can use the same variable that you created in 3!

```{r}
# longest flipper length

max(flipperLength, na.rm=TRUE)

# shortest flipper length

min(flipperLength, na.rm=TRUE)

```

5.  What is the range of bill depths of penguins? (Range is the maximum value - minimum value)

```{r}
billDepth<-penguins$bill_depth_mm

# deepest bill depth

deepest<-max(billDepth, na.rm=TRUE)


# shallowest bill depth

shallowest<-min(billDepth, na.rm=TRUE)

# range of bill depth

range<-deepest - shallowest

range

```

6.  How many species of penguins are in this data set (hint: there is a function to find distinct values in a vector)? List them using comments.

```{r}
# get unique values
species<-unique(penguins$species)

# count them
length(species)

```

7.  Find the value for the longest bill in the data set. Assign it to the variable longestBill.

```{r}

longestBill<-max(penguins$bill_length_mm, na.rm=TRUE)

longestBill

```

8.  Calculate the variance of body mass. (Hint: google variance in R)

```{r}

var(penguins$body_mass_g, na.rm=TRUE)


```

9.  Calculate the variance of flipper length.

```{r}

var(penguins$flipper_length_mm, na.rm=TRUE)

```

10. Calculate and compare the standard deviation of bill length and bill depth. Which has a larger standard deviation?

```{r}
# standard deviation of bill length

sd(penguins$bill_length_mm, na.rm=TRUE)

# standard deviation of bill depth

sd(penguins$bill_depth_mm, na.rm=TRUE)

# Which has a larger standard deviation? 

#Answer: the standard deviation for bill length is larger.

```

11. Challenge: calculate the mean and standard deviation of bill length for gentoo penguins

```{r}

library(tidyverse)

gentoo<-filter(.data=penguins, species=="Gentoo")

mean(gentoo$bill_length_mm, na.rm=TRUE)

sd(gentoo$bill_length_mm, na.rm=TRUE)

```
