---
title: "Homework Module 2.1"
format: html
---


### Your Name

### Date



In the questions below, use R code to answer questions. For any non-coding questions, give your answer as a comment.

Run this code chunk first, to make the data set from the code along is available as the variable `sick`:

```{r}
library(tidyverse)
sick<-read_csv("sick_data.csv")
```

1.  What does "gg" in "ggplot" stand for? What are the three components of data visualizations?

```{r}



```

2.   Create a histogram of the distribution of team member weights with ggplot. Make sure you add descriptive labels.

```{r}




```

3.  Create a scatter plot displaying participant weight with percent plant intake using ggplot. Label axes appropriately.

```{r}




```

4.  Describe why you might use a histogram, scatter plot, or bar plot (i.e. what is the purpose of each?).

```{r}



```

5.  Generate a bar plot showing the average fish consumption among those who specialize in Management, Genetics, and Medicine. Include labels, and use the "fill" attribute to generate colors and a legend.

```{r}




```


6. For each of the three plots above, write code to save the files to "histogram.jpg", "scatterplot.jpg", and "barplot.jpg". (Hint: assign each plot to a variable as part of your answer)

```{r}





```
