---
title: "Code-a-long 2.2"
output: html
---

### Learning Outcomes


-   Students will be able to use ggplot to generate box plots.
-   Students will be able to apply error bars to box plots and bar plots.



```{r}
library(tidyverse)

library(palmerpenguins)

penguins<-palmerpenguins::penguins

penguins



```

### Box plots with error bars

Strategy: Use geom_boxplot(), and in the aes function, set x equal to a categorical column, which will automatically group them. For the horizontal lines (error bars), add stat_boxplot(geom = "errorbar").

```{r}





```

### Bar plots with error bars

Strategy: use group_by/summarize to calculate group mean and standard deviation. Add geom_errorbar, in which the top top bar is the mean + standard deviation, and the lower bar is the mean - standard deviation:

```{r}




```

### Practice

Create a box plot comparing penguin mass among species. Include error bars, a legend, and labels.

```{r}
# create box plot below



```

Create a bar plot comparing penguin mass among species. Include error bars (+/- 1 sd), a legend, and labels.

```{r}
# create bar plot below





```
